Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-18 Documents/supplementary_text.tex
More hacking on supplement.

We developed a continuous-time, compartmental model consisting of 8
health states (\autoref{model_diag}): susceptible to HIV infection
($S$), vaccinated against HIV ($R$), acute HIV infection ($A$),
undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
($D$), treated without viral suppression ($T$), viral suppression
($V$), and having AIDS ($W$).  Transitions between states are governed
by a series of differential equations parametrized using rates
estimated from other studies and from incidence and prevalence data
(Table \ref{model_param}).  The model is deterministic, but
uncertainty in the parameters is treated by running the model with
many different samples from the parameter distributions.

@@

\begin{table}
  \begin{center}
    \begin{tabularx}{\textwidth}{lXlll}
      \hline
      & Definition & Value & Reference \\
      \hline
      $\delta$	& Rate of leaving acute infection
      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
      & \cite{Hollingsworth2008-iy} \\
      $\sigma$	& Rate of developing AIDS without viral suppression
      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
      $\theta$ & Rate of developing AIDS with viral suppression
      & See eq.~(\ref{theta}) & --- \\
      $\gamma$ & Rate of viral suppression
      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
      & \cite{Currie2009-yz} \\
      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
      & \cite{Morgan2002-cq} \\
      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
      $\omega$	& Reduction in lifetime with viral suppression
      & $\Uniform$(5, 8)\;y
      & \cite{Unaids2014-ue, Samji2013-kf} \\
      $\tau_{A}$ & Transmissibility during acute phase
      & $\Triangular$(0.0039, 0.0082, 0.0150)
      & \cite{Skarbinski2015-ni,Wawer2005-us}\\
      $\tau_{U}$ & Transmissibility after acute phase
      & $\Triangular$(0.00077, 0.0014, 0.00251)
      & \cite{Hughes2012-so} \\
      $\varepsilon$ & Relative transmissibility with
      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
      & \cite{Donnell2010-xo} \\
      $n$ & Sex acts per year & $\Uniform$(96, 108)
      & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\
      $\mu$ & Background death rate & Country specific
      & \cite{World_Development_Indicators2013-ee} \\
      $B$ & Birth rate & Country specific
      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
      $\alpha$ & Diagnosis rate & See eqs.~(\ref{target_rates}) & --- \\
      $\phi$ & Treatment rate & See eqs.~(\ref{target_rates}) & --- \\
      $\psi$ & Rate of relapse to untreated & See eqs.~(\ref{target_rates})
      & --- \\
      $\zeta$ & Vaccination rate & See eqs.~(\ref{target_rates}) & --- \\
      \hline
    \end{tabularx}
    \caption{Model parameters. $\Triangular$, $\Uniform$,
      and $\BetaPERT$ are sampling distributions: see text for a
      full description.  For vaccine efficacy, $50\%$ was the
      baseline, and $30\%$ and $70\%$ were also used in scenario
      analysis.}
    \label{model_param}
  \end{center}
\end{table}

Birth and death.

>>>>

We developed a continuous-time, compartmental model that divides
people aged 15 years and older into 8 health states
(\autoref{model_diag}): susceptible to HIV infection ($S$), vaccinated
against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
infection ($U$), diagnosed but untreated HIV infection ($D$), treated
without viral suppression ($T$), viral suppression ($V$), and having
AIDS ($W$).  We chose to consider only people aged 15 years and older
because they are the vast majority of PLHIV (93\% in 2014
\cite{UNICEF}).  Transitions between states are governed by a series
of differential equations parametrized using rates estimated from
other studies and from incidence and prevalence data (Table
\ref{model_param}).  The model is deterministic, but uncertainty in
the parameters is treated by running the model with many different
samples from the parameter distributions and summarizing the model
outcomes using the median, 1st and 3rd quartiles (i.e., 25th and 75th
percentiles), and 5th and 95th percentiles.

@@

\begin{table}
  \begin{center}
    \begin{tabularx}{\textwidth}{lXlll}
      \hline
      & Definition & Value & Reference \\
      \hline
      $\mu$ & Background death rate & Country specific
      & \cite{World_Development_Indicators2013-ee} \\
      $B$ & Recruitment rate & Country specific
      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
      $\delta$	& Rate of leaving acute infection
      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
      & \cite{Hollingsworth2008-iy} \\
      $\sigma$	& Rate of developing AIDS without viral suppression
      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
      $\theta$ & Rate of developing AIDS with viral suppression
      & See eq.~(\ref{theta}) & --- \\
      $\gamma$ & Rate of viral suppression
      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
      & \cite{Currie2009-yz} \\
      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
      & \cite{Morgan2002-cq} \\
      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
      $\omega$	& Reduction in lifetime with viral suppression
      & $\Uniform$(5, 8)\;y
      & \cite{Unaids2014-ue, Samji2013-kf} \\
      $\tau_{A}$ & Transmissibility during acute phase
      & $\Triangular$(0.0039, 0.0082, 0.0150)
      & \cite{Skarbinski2015-ni,Wawer2005-us}\\
      $\tau_{U}$ & Transmissibility after acute phase
      & $\Triangular$(0.00077, 0.0014, 0.00251)
      & \cite{Hughes2012-so} \\
      $\varepsilon$ & Relative transmissibility with
      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
      & \cite{Donnell2010-xo} \\
      $n$ & Sex acts per year & $\Uniform$(96, 108)
      & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\
      $\alpha$ & Diagnosis rate & See eqs.~(\ref{target_rates}) & --- \\
      $\phi$ & Treatment rate & See eqs.~(\ref{target_rates}) & --- \\
      $\psi$ & Rate of relapse to untreated & See eqs.~(\ref{target_rates})
      & --- \\
      $\zeta$ & Vaccination rate & See eqs.~(\ref{target_rates}) & --- \\
      \hline
    \end{tabularx}
    \caption{Model parameters. $\Triangular$, $\Uniform$,
      and $\BetaPERT$ are sampling distributions: see text for a
      full description.  For vaccine efficacy, $50\%$ was the
      baseline, and $30\%$ and $70\%$ were also used in scenario
      analysis.}
    \label{model_param}
  \end{center}
\end{table}

The background mortality rate ($\mu$) in each of the 127 countries was
collected from published estimates
\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
the 15 age group was 
including population
growth rate \cite{WorldBankpg}, death rate
\cite{World_Development_Indicators2013-ee}, and number of people aged
15--49 years \cite{The_World_Bank2016-fd}
